\documentclass[UTF8,a4paper,12pt]{ctexart}

\usepackage{geometry}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{multirow}
\usepackage{array}
\usepackage{tabularx}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{amsmath}
\usepackage{titlesec}
\usepackage{caption}
\usepackage[numbers,sort&compress]{natbib}
\usepackage{fancyhdr}
\usepackage{setspace}
\usepackage{tikz}
\usepackage{algpseudocode}

\usetikzlibrary{positioning, arrows.meta, fit, backgrounds}
\geometry{margin=2.4cm}
\hypersetup{colorlinks=true, linkcolor=black, citecolor=black, urlcolor=blue}
\setlength{\parindent}{2em}
\setlength{\parskip}{0pt}
\setlength{\emergencystretch}{3em}
\setlist{nosep}
\captionsetup{font=small, labelfont=bf}
\renewcommand{\bibname}{参考文献}
\renewcommand{\refname}{参考文献}
\renewcommand{\arraystretch}{1.15}

% -- Float placement: keep figures/tables with surrounding text --
\renewcommand{\topfraction}{0.85}
\renewcommand{\bottomfraction}{0.75}
\renewcommand{\textfraction}{0.10}
\renewcommand{\floatpagefraction}{0.80}
\setcounter{topnumber}{3}
\setcounter{bottomnumber}{2}
\setcounter{totalnumber}{5}
\setlength{\intextsep}{8pt plus 2pt minus 2pt}
\setlength{\floatsep}{10pt plus 2pt minus 2pt}
\setlength{\textfloatsep}{12pt plus 2pt minus 4pt}

\newcolumntype{L}[1]{>{\raggedright\arraybackslash}p{#1}}
\newcolumntype{Y}{>{\raggedright\arraybackslash}X}
\usetikzlibrary{arrows.meta,calc,fit,positioning,shapes.geometric}
\newcounter{algorithm}
\renewcommand{\thealgorithm}{\arabic{algorithm}}

% -- CCCF style: Chinese numeral section headings (一、二、三...) --
\renewcommand{\thesection}{\chinese{section}}
\titleformat{\section}{\centering\heiti\zihao{-3}}{\thesection、}{0em}{}
\titleformat{\subsection}{\heiti\zihao{4}}{\arabic{section}.\arabic{subsection}}{0.6em}{}
\titleformat{\subsubsection}{\heiti\zihao{-4}}{\arabic{section}.\arabic{subsection}.\arabic{subsubsection}}{0.5em}{}

\titlespacing*{\section}{0pt}{1.2em}{0.8em}
\titlespacing*{\subsection}{0pt}{0.8em}{0.4em}
\titlespacing*{\subsubsection}{0pt}{0.6em}{0.3em}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot[C]{\thepage}
\renewcommand{\headrulewidth}{0pt}

\begin{document}

% ===========================================
% Title block (following CCCF 2601 reference style)
% ===========================================
\begin{center}
{\bfseries\zihao{2} 国产算力平台大模型推理引擎综述\par}
\vspace{0.95em}
{\zihao{4} 张书豪\textsuperscript{1}，廖小飞\textsuperscript{1}\par}
\vspace{0.45em}
{\zihao{5} \textsuperscript{1}大数据技术与系统国家地方联合工程研究中心\par}
{\zihao{5} 服务计算技术与系统教育部重点实验室\par}
{\zihao{5} 集群与网格计算湖北省重点实验室\par}
{\zihao{5} 华中科技大学计算机科学与技术学院\par}
\end{center}

\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\footnotetext[1]{受新一代人工智能国家科技重大专项资助（课题编号：2025ZD0123804）\\ 通信作者：廖小飞，E-mail：xfliao@hust.edu.cn}
\renewcommand{\thefootnote}{\arabic{footnote}}

\vspace{0.6em}

\begin{spacing}{1.2}

% ===========================================
% Body (no abstract at top — CCCF style puts abstract at end)
% ===========================================
\input{sections/01_introduction}
\input{sections/02_domestic_ecosystem}
\input{sections/03_architecture}
\input{sections/04_engines}
\input{sections/05_challenges}
\input{sections/06_outlook}
\input{sections/07_conclusion}

% ===========================================
% Author bio (CCCF style: before references)
% ===========================================
\vspace{1em}
\noindent\begin{minipage}{\linewidth}
\noindent % Author photo placeholder
\textbf{金海}~~CCF会士、副理事长。华中科技大学计算机学院教授。主要研究方向为计算机体系结构、计算系统虚拟化、集群计算和云计算、并行I/O。hjin@hust.edu.cn
\end{minipage}

\vspace{1.2em}

% ===========================================
% References
% ===========================================
\begingroup
\sloppy
\bibliographystyle{unsrtnat}
\bibliography{refs}
\endgroup

% ===========================================
% English title, abstract & keywords (CCCF style: at end)
% ===========================================
\vspace{1.5em}
\noindent\textbf{\large A Survey of Large-Model Inference Engines on Domestic Computing Platforms}

\vspace{0.6em}
\noindent\textbf{Zhang Shuhao, Liu Shifeng, Du Yufeng, Ma Junhao, Qiu Ruijie, Liao Xiaofei, Jin Hai}

\vspace{0.6em}
\noindent\textbf{Abstract}\quad This survey examines large-model inference engines on domestic computing platforms. Using cross-checkable public evidence, it explains why the ecosystem has split into three routes---upstream-core reuse and enhancement, vertically integrated platform stacks, and domestic-native systems---and adopts an analytical scaffold comprising a unified abstraction/observability base plus three main paths (execution and communication, state governance, compression-cost co-optimization) to compare where each route places its primary complexity. The survey distills structural challenges around hardware heterogeneity, complex workloads, unstable compression gains, and rapid upstream evolution, and outlines future directions including platform capability contracts, state-centric runtime restructuring, and unified control-plane governance.

\vspace{0.4em}
\noindent\textbf{Key Words}\quad domestic computing platforms; large-model inference; inference engine; runtime systems; hardware-software co-design

% ===========================================
% Chinese abstract & keywords (CCCF style: at end)
% ===========================================
\vspace{1.2em}
\noindent\textbf{摘要}\quad 本文面向国产算力平台上的大模型推理引擎，围绕"生态格局—分析骨架—路线比较—关键挑战—未来收敛"这一主线展开结构化综述。以可交叉核验的公开证据为基础，本文首先梳理当前生态为何分化为开源主干复用增强、平台一体化方案与国产原生/独立路线三类，继而以"一个底座（统一抽象与可观测证据链）、三条主路径（执行与通信、状态治理、压缩与成本协同）"为分析骨架，比较不同路线把复杂度主要压在何处。在此基础上，将平台异构、复杂任务负载、压缩收益不稳定、上游快速演进与评测体系失真等问题收敛为结构性挑战，并讨论能力契约沉淀、状态中心化运行时重构和控制面一体化治理等未来方向，以期为国产推理引擎的路线选择与架构演进提供可复核的分析框架。

\vspace{0.4em}
\noindent\textbf{关键词}\quad 国产算力平台；大模型推理；推理引擎；运行时；软硬协同

\vspace{0.4em}
\noindent\textbf{中图分类号：}TP39

\end{spacing}

\end{document}
